### 2021-12-03 lmcs/appendix.tex
Update appendix.tex

% !TeX root = priorities.tex
\section{Priority GV}
\begingroup
\usingnamespace{pgv}
\restatelemma{lempgvvaluedone}
\input{prf/lem-pgv-value-done}

\restatelemma{lempgvsubstitution}
\input{prf/lem-pgv-substitution}

\restatelemma{lempgvsubjectreductionterms}
\input{prf/lem-pgv-subject-reduction-terms}

\restatelemma{lempgvsubjectcongruence}
\input{prf/lem-pgv-subject-congruence}

\restatetheorem{thmpgvsubjectreductionconfs}
\input{prf/thm-pgv-subject-reduction-confs}

\begin{restatablelemma}{lempgvreadypriority}
  \label{lem:pgv-ready-priority}
  If $\tseq[\cs{p}]{\ty{\Gamma}}{L}{T}$ is ready to act on $\tmty{x}{S}\in\ty{\Gamma}$, then the priority bound $\cs{p}$ is some priority $\cs{o}$, \ie not $\cs{\pbot}$ or $\cs{\ptop}$.
\end{restatablelemma}
\begin{proof}
  Let $\tm{L}=\tm{\plug{E}{M}}$. By induction on the structure of $\tm{E}$. $\tm{M}$ has priority $\pr({\ty{S}})$, and each constructor of the evaluation context $\tm{E}$ passes on the \emph{maximum} of the priorities of its premises. No rule introduces the priority bound $\cs{\ptop}$ on the sequent.
\end{proof}

\restatelemma{lempgvcanonicalforms}
\begin{proof}
  We move any $\nu$-binders to the top using \LabTirName{SC-ResExt}, discard any superfluous occurrences of $\tm{\child\;\unit}$ using \LabTirName{SC-ParNil}, and move the main thread to the rightmost position using \LabTirName{SC-ParComm} and \LabTirName{SC-ParAssoc}.
\end{proof}

\restatetheorem{thmpgvclosedprogressconfs}
\input{prf/thm-pgv-closed-progress-confs}

\input{fig/pgv-typing-sugar}
\endgroup

>>>>

% !TeX root = priorities.tex
% \section{Priority GV}
% \begingroup
% \usingnamespace{pgv}
% \restatelemma{lempgvvaluedone}
% \input{prf/lem-pgv-value-done}

% \restatelemma{lempgvsubstitution}
% \input{prf/lem-pgv-substitution}

% \restatelemma{lempgvsubjectreductionterms}
% \input{prf/lem-pgv-subject-reduction-terms}

% \restatelemma{lempgvsubjectcongruence}
% \input{prf/lem-pgv-subject-congruence}

% \restatetheorem{thmpgvsubjectreductionconfs}
% \input{prf/thm-pgv-subject-reduction-confs}

% \begin{restatablelemma}{lempgvreadypriority}
%   \label{lem:pgv-ready-priority}
%   If $\tseq[\cs{p}]{\ty{\Gamma}}{L}{T}$ is ready to act on $\tmty{x}{S}\in\ty{\Gamma}$, then the priority bound $\cs{p}$ is some priority $\cs{o}$, \ie not $\cs{\pbot}$ or $\cs{\ptop}$.
% \end{restatablelemma}
% \begin{proof}
%   Let $\tm{L}=\tm{\plug{E}{M}}$. By induction on the structure of $\tm{E}$. $\tm{M}$ has priority $\pr({\ty{S}})$, and each constructor of the evaluation context $\tm{E}$ passes on the \emph{maximum} of the priorities of its premises. No rule introduces the priority bound $\cs{\ptop}$ on the sequent.
% \end{proof}

% \restatelemma{lempgvcanonicalforms}
% \begin{proof}
%   We move any $\nu$-binders to the top using \LabTirName{SC-ResExt}, discard any superfluous occurrences of $\tm{\child\;\unit}$ using \LabTirName{SC-ParNil}, and move the main thread to the rightmost position using \LabTirName{SC-ParComm} and \LabTirName{SC-ParAssoc}.
% \end{proof}

% \restatetheorem{thmpgvclosedprogressconfs}
% \input{prf/thm-pgv-closed-progress-confs}

% \input{fig/pgv-typing-sugar}
% \endgroup
